---
title: "rsv_inter_R"
author: "David Hodgson"
date: "24/09/2020"
output: html_document
---

This is an R-based implementation of the cpp code used in Hodgson et al. 2021

# 1. Setup 
## 1.1 Import libraries
May need to downoad all of these (use install.packages).

```{r libraries}

library(Rcpp)
library(RcppEigen) 
library(coda) 
library(tidyverse)
library(parallel)
library(MASS)
library(foreach)
library(gridExtra)
library(doParallel)
library(devtools)
library(here)
library(patchwork)
library(here)

```


## 1.2 Import data for the epidemic model intervention model

This section calls a class from the cpp module inteface (RunInterventions.cpp) for the cpp intervention model (defined in RunInterventions.h).
Then, using demographic data from the UK (ukdata) and model data needed for the intervention programmes (data_inter_uk), the intervention model class is initialised and ready to use! 

```{r}

sourceCpp(here("src", "RunInterventions.cpp")) # Uploads empty RunInterventions class
source(here("R", "RunInterventionsClass.R")) # Uploads emmake_RunInterventionspty function
burnin_yrs <- 2 # two year burn-in
run_yrs <- 10 # 10-year run

# Load premade datasets
load(file = here::here("data", "inter_model_input", "rsv_data_uk.RData")) # loads ukdata
load(file = here::here("data", "inter_model_input", "inter_data_uk.RData")) # loads data_inter_uk

classRunInterventions <- make_RunInterventions(RunInterventions, ukdata, data_inter_uk, burnin_yrs * 365, run_yrs * 365)

```

# 2. Code to run the intervention programmes from Hodgson et al. 
## 2.1 Get the descriptions of the 16 programes.

This section saves all the infomation needed to run the 16 intevention progammes in `data/inter_model_input/hodgson_programmes.RData` 

```{r}

# Load relevant R scripts
source("R/vac_cal.R")         # Generates the vaccination calendars
source("R/calc_outcomes.R")   # Calculate the outcomes
source("R/remake_hodgson.R")  # Vaccination specifics for hodgson et al.
load(here("data", "inter_model_output", "posteriors.Rda")) # posteriors from fitting in Hodgson et al. 2020

# Load seed values
seeds <- read.csv(here("data", "inter_model_input", "seed_samples.csv"), header = FALSE)[, 1] + 1
seed_len <- seq_len(1249)
vac_par_info <- list(om_mab = 1 / 250, direct = FALSE, xi_boost = 1)

all_eff <- list(
  pal_eff = rweibull(length(seed_len), 12.4311, 0.772251),
  mab_eff = rweibull(length(seed_len), 11.8975, 0.7317),
  lav_eff = rweibull(length(seed_len), 31.4637, 0.844676),
  mat_eff = rweibull(length(seed_len), 3.32676, 0.461343)
)

# Create calendars and save
create_calendars_hodgson(all_eff)

```

# 3. Run the 16 intervention programmes

```{r}

# Load relevant R scripts
source("R/vac_cal.R") # generates the vaccination calendars
source("R/calc_outcomes.R") # calculate the outcomes
load(here("data", "inter_model_output", "posteriors.Rda")) # posteriors from fitting in Hodgson et al. 2020
seeds <- read.csv(here("data", "inter_model_input", "seed_samples.csv"), header = FALSE)[, 1] + 1 # load seeds
load( file = here::here("data", "inter_model_input", "hodgson_programmes.RData")) # load all_info

prog_names <- names(all_info$programmes)
all_programmes <- all_info$programmes
cov_c <- all_info$mat_cov
outputs <- vector(mode = "list", length = length(prog_names))

for (i in 1:16) {
  outputs[[i]] <- run_sample_custom(seeds[1:1000], all_programmes[[prog_names[i]]], vac_par_info, cov_c[i], post)
}

save(outputs, file = here::here("data", "inter_model_output", "all_prog_sim.RData"))

```

Check the intervention costs
```{r}

outputs[[10]]$vac_cal[1:52, 3] %>% sum # 251,161 doses a year for LAV
outputs[[10]]$vac_cal[1:52, 1] %>% sum # 2128.624 doses a year Palivizumab

outputs[[10]]$cost %>% filter(metric == "inter", type == "undiscounted") # cost is over 10 years £23828482
251161 * 9 * 10 # 22604490 for LAV
2128 * 54 * 10 # 1149120 for Palivizumab
22604490 + 1149120 # 23753610 (similar to quoted cost)

```

```{r}


#load(file = here("data", "inter_model_output", "inter_all_outcome.RData") )# outcomes_all
#load(file = here("data", "inter_model_output", "inter_all_econ.RData") )# econmetric_alll
load(file = here::here("data", "inter_model_output", "all_prog_sim.RData")) # outputs
load(file = here("data", "cpp_model_output", "outcomes_all.RDS"))
programmes <- df_outcomes$health_outcomes %>% pull(inter) %>% unique
#post process results of simualtion
df_R_plot_list <- list()
df_R_qaly_list <- list()
df_R_cost_treat_list <- list()
df_R_cost_admin_list <- list()

for (i in 1:16) {
  df_R_plot_list[[i]] <- outputs[[i]]$outcomes_week_age %>%
    group_by(outcome, seed, age_group) %>%
    summarise(incidence = sum(incidence)) %>%
    mutate(outcome = case_when(
        outcome == "all_cases"~"All cases",
        outcome == "symptomatic_cases"~"Symptomatic cases",
        outcome == "gp_visits"~"GP visits",
        outcome == "bed_days"~"Bed days",
        outcome == "hospital_cases"~"Hospitalised cases",
        outcome == "deaths"~"Deaths"
        )) %>%
      mutate(programme = programmes[i], type = "R") %>% rename(value = incidence)

    df_R_qaly_list[[i]] <- outputs[[i]]$QALY %>%
      filter(metric == "total", type == "discounted") %>%
      dplyr::select(metric, seed, value) %>%
      mutate(programme = programmes[i]) %>% rename(inter = programme)

    df_R_cost_treat_list[[i]] <- outputs[[i]]$cost %>%
      filter(metric == "direct", type == "discounted") %>%
      dplyr::select(metric, seed, value) %>%
      mutate(programme = programmes[i]) %>% rename(inter = programme)

    df_R_cost_admin_list[[i]] <- outputs[[i]]$cost %>%
      filter(metric == "inter", type == "discounted") %>%
      dplyr::select(metric, seed, value) %>%
      mutate(programme = programmes[i]) %>% rename(inter = programme)
}

df_R_plot <- bind_rows(df_R_plot_list)
df_R_qaly <- bind_rows(df_R_qaly_list)
df_R_cost_treat <- bind_rows(df_R_cost_treat_list)
df_R_cost_admin <- bind_rows(df_R_cost_admin_list)

output_lucy <- list(outcomes = df_R_plot, qaly = df_R_qaly, cost_treat = df_R_cost_treat, cost_admin = df_R_cost_admin)
save(output_lucy, file = here::here("data", "other", "df_outcomes_lucy.RData"))


load(file = here::here("data", "other", "df_outcomes_lucy.RData"))
output_lucy$outcomes %>% pull(outcome) %>% unique

outputs[[2]]$outcomes_week_age %>% filter(seed == 566) 
output_lucy$outcomes %>% filter(seed == 887) %>% dplyr::filter(outcome == "All cases", age_group == 25)
output_lucy$qaly %>% filter(seed == 887) 
output_lucy$cost_treat %>% filter(seed == 887) 

output_lucy$outcomes %>% filter(seed == 1)


output_lucy$outcomes[!complete.cases(output_lucy$outcomes), ] %>% as.data.frame %>% dplyr::select(!age_group) %>% unique %>% pull(seed) %>% unique

left_join(
  df_R_qaly %>% filter(inter == "NONE") %>% rename(value_base = value) %>% dplyr::select(!inter),
  df_R_qaly %>% filter(inter == "PAL_VHR_S")
) %>% mutate(QALY_diff = value_base - value)

 
```
